---
title: "Contact"
format:
  html:
    page-layout: full
    toc: false
date: today
language:
  title-block-published: "Last modified"
---

<style>
#title-block-header,
#quarto-header,
#quarto-header-headroom {
  display: none !important;
}
</style>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(htmltools)
source("R/site_components.R")
coverage_file_date <- get_latest_coverage_date()
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
site_header()
```

```{=html}
<section class="column-screen subpage-hero-band">
  <div class="subpage-hero-copy">
    <p class="subpage-eyebrow">Resources</p>
    <h1>Contact</h1>
    <p class="subpage-hero-lede">Use this page to report missing coverage, flag errors, or point us to jurisdictional updates that should be reflected in the maps.</p>
  </div>
</section>
<div class="subpage-main">
```

::: {.subpage-copy-wide}
If you find errors or know of ALS coverage that should be added to the maps, please open an issue in the repository or contact the project team directly.
:::

::: {.subpage-summary-grid}
::: {.subpage-summary-card}
### GitHub issues

Report a problem or suggest a correction through the [project issue tracker](https://github.com/ptompalski/CanadaForestLidarCoverage/issues/new).
:::

::: {.subpage-summary-card}
### Direct contacts

Piotr Tompalski: piotr.tompalski\@nrcan-rncan.gc.ca

Joanne White: joanne.white\@nrcan-rncan.gc.ca
:::
:::

```{=html}
</div>
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
site_footer(coverage_file_date)
```
