---
title: "Data"
format: html
engine: knitr
date: 09/17/2024
date-modified: today
---

```{r, echo=F, warning=F, message=F}
source("R/0000_setup.R")
library(kableExtra)

# find the most recent shapefile in each provincial folder

getNewestFileDate <- function(dir) {
  
  PATH <- glue::glue("../5_lidarStatusCanada/layers/{dir}/")
  
  flist <- fs::dir_ls(PATH , recurse = T, glob = "*.shp$") %>% lapply(file.info) %>% bind_rows() %>% arrange(desc(ctime))
  return(as_date(flist[1,]$ctime))
  
}

tbl_updates <- tibble(Jurisdiction = c("BC", "AB", "SK", "ON", "QC", "NB", "PE","NS")) %>%
  mutate(`Last update` = map(Jurisdiction, getNewestFileDate)) %>%
  unnest(`Last update`) 
```



## ALS coverage data sources

The data used in this compilation was obtained from a number of sources including online services and by directly contacting Provincial and Territorial departments responsible for data management. Because some of the coverage data are not available for the public, the vector layers presented on this website cannot be shared. 

The table below lists the sources of coverage data by jurisdiction. Note that "Last update" corresponds to the date the coverage map for each jurisdiction was updated, and is not indicative of the most recent ALS acquisition.

```{r, echo=F, warning=F, message=F}
#| tbl-colwidths: [10, 15, 75]

theFootnote <- "\"Last update\" corresponds to the date the coverage map for each jurisdiction was updated, and is not indicative of the most ALS acquisition."

tribble(
  ~Jurisdiction, ~`Data source`,
  
  "BC",
  "BC Ministry of Forests and [lidar.gov.bc.ca](https://lidar.gov.bc.ca/). ",
  
  "AB",
  "AB Forestry and Parks, Alberta Biodiversity Monitoring Institute (ABMI)",
  
  "SK",
  "SK Ministry of Environment",
  
  "ON",
  "Ministry of Natural Resources",
  
  "QC",
  "Ministère des Ressources naturelles et des Forêts",
  
  "NB",
  "NB Natural Resources and Energy Development, and [www.snb.ca/geonb1](http://www.snb.ca/geonb1/e/dc/catalogue-E.asp)",
  
  "PE",
  "Prince Edward Island Department of Environment, Energy and Climate Action", #https://www.gov.pe.ca/gis/index.php3?number=1011267&lang=E
  
  "NS",
  "[nsgi.novascotia.ca/datalocator](https://nsgi.novascotia.ca/datalocator/elevation/) and Department of Natural Resources and Renewables"
  
  
) %>% left_join(tbl_updates) %>%
  relocate(`Data source`,.after = last_col()) %>%
  kable() 
 
  # kableExtra::footnote(general = theFootnote) %>%
  # kable_classic() %>% 
```





## ALS data availability

```{r, echo=F, warning=F, message=F}

#| tbl-colwidths: [15, 85]

tribble(
  ~Jurisdiction, ~`Data sharing policy`,
  
  "BC",
  "ALS - open data.<br>DEM and CHM from systematic provincial acquisition will be shared. <br>[www.lidar.gov.bc.ca](https://www.lidar.gov.bc.ca)",
  
  "AB", 
  "GoA: Initial provincial coverage ALS data and derivatives were acquired with a licence (i.e., data were leased for 99 years). Sharing is limited to GoA partners (e.g. academia) for collaborative projects and forest industry. <br>Industry: 11 projects between 2017 and 2022 funded through the Forest Resource Improvement Program (FRIP). Data are not currently open, although FRIP is public funds. <br>ABMI acquisitions [will be made freely available](https://abmi.ca/home/news-events/news/Open-Lidar-Data-Announcement.html?mode=detail&scroll).",

  
  "SK", 
  "ALS point clouds currently not shared as open data.<br>Derivatives (DEM) are shared openly (not all derived from lidar): [environment-saskatchewan.hub.arcgis.com](https://environment-saskatchewan.hub.arcgis.com/pages/forest_resource_inventory)", 
  "ON", 
  "ALS point clouds and derivatives (DEM, CHM, DSM) are open data, available at  [geohub.lio.gov.on.ca](https://geohub.lio.gov.on.ca/maps/lio::forest-resources-inventory-leaf-on-lidar/about)",
  
  "QC", 
  "ALS data available for purchase ([geoboutique.mern.gouv.qc.ca](http://geoboutique.mern.gouv.qc.ca/)).<br>Derivatives (DEM, CHM, hillshade, slope) available as open data: [https://www.donneesquebec.ca/](https://www.donneesquebec.ca/)",
  
  "NB",
  "ALS data are open and available for download: [www.snb.ca/geonb1/e/dc/lidar.asp](http://www.snb.ca/geonb1/e/dc/lidar.asp).<br>Derivatives (i.e. DEM, CHM, hillshade, slope) are open and are available as [WMS/WCS service](https://www2.gnb.ca/content/gnb/en/departments/erd/open-data/raster-data.html#12).",
  
  "PE", 
  "ALS data and derivatives available on request.<br>DEM available as open data (via HRDEM): [](https://open.canada.ca/data/en/dataset/957782bf-847c-4644-a757-e383c0057995).",
  # "https://ftp.maps.canada.ca/pub/elevation/dem_mne/highresolution_hauteresolution/dtm_mnt/1m/PEI/Prince_Edward_Island_2020/",
  
  "NS", 
  "ALS files and derivatives are open data ([nsgi.novascotia.ca/datalocator/elevation/](https://nsgi.novascotia.ca/datalocator/elevation/))."
  
) |>  
  
  knitr::kable(escape=F)  
```


## Additional ALS datasets in Canada

ALS data acquired outside of forest ecosystems (e.g.,  in urban areas or for flood mapping purposes)  or for research purposes are not included in the maps and summaries above. Some of those datasets include:

- [High Resolution Digital Elevation Model (HRDEM) - CanElevation Series](https://open.canada.ca/data/en/dataset/957782bf-847c-4644-a757-e383c0057995)
- [Petawawa Research Forest](https://opendata.nfis.org/mapserver/PRF.html)
